Universal Anonymous Signatures

### 2022-06-15 prism-backend/research/gsac/app-model-related.tex
Seemingly valid construction of DAC from UAS. Proof pending.

\todo{Naming gets a bit confusing here, as \cite{fhs19} use \opk as ``organization
  public key'' and we use it as ``opener public key'', etc. Make some renaming
  (probably, adopt our naming convention).}

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure). Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ and $UserKeyGen$ algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \cite{fig:model-ac}, with inocuous adaptations to
make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        (\opk,\osk) \gets OrgKeyGen(1^\secpar) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,D) \rangle \\
        \pcif b = 1 \land \forall j: \OWNR[j] \in \CU
        \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

\subsubsection{\CUASAC Construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
function, is a secure anonymous credential scheme according to the \cite{fhs19}
model. We first quickly define the algorithms, and then prove security. Note
that, for better alignment with \UAS, we add a common setup process which is
part of $OrgKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
security-wise, though.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk')$.
\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

We give a simple definition for delegatable anonymous credentials extending
the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
show that it satisfies our basic notion of delegatable anonymous credentials.
Roughly, a delegatable anonymous credential scheme is an anononymous credential
scheme in which every issuer of level $n$ can only issue credentials of level
$n+1$. For simplicity, we restrict to the case of using only one credential per
signature, but the generalization is trivial. Note that, in addition to the
algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
which, given an issuer's public key and its alleged level, returns $1$ if the
level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\        
        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
        D \cup \lbrace n+1 \rbrace)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
        \not\subseteq \ATTR[j])~\lor\\
        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

>>>>

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure). Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \cite{fig:model-ac}, with inocuous adaptations to
make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

\subsubsection{\CUASAC Construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
function, is a secure anonymous credential scheme according to the \cite{fhs19}
model. We first quickly define the algorithms, and then prove security. Note
that, for better alignment with \UAS, we add a common setup process which is
part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
security-wise, though.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with $\opk'$ from \parm as opener public key.
\end{description}

@@

To showcase the feasibility of building delegatable anonymous credentials (DAC)
from \UAS, we give a simple definition for a DAC scheme, extending
\cite{fhs19} and inspired by \cite{bcc+09}. Note however that, unlike the
latter, our simple scheme built from \CUASGen does not ensure privacy of the
delegation chain -- but it does, however, ensure that a (not top-level) issuer
can only delegate attributes contained in a credential it owns. Also, for
simplicity, we restrict to the case of using one credential per
signature/interactive credential presentation, and assume that all parties use
the same opener and \finsp function.
%
The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $Obtain,Issue$ and
$Show,Verify$ interactive protocols.
%
In the modelling for this setting, since there are multiple issuers, in addition
to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are as before. For unforgeability, we still require
that no adversary can authenticate using a set of attributes that have not been
issued to a corrupt user. In addition, we require that for any possible
successful authentication protocol using a level-$n$ credential, we can extract
a chain of credentials of length $n$ such that each level-$i$ credential can
be used successfully to authenticate a level-$(i+1)$ credential up to the
level-$n$ credential, and that the attributes revealed in the level-$n$
authentication are contained in all the credentials up the chain.

% \todo{Rewrite when the full rewriting of the paper is done. For now, just
%   adapting the construction.}
% We give a simple definition for delegatable anonymous credentials extending
% the anonymous credential model in \cite{fhs19}, but drawing inspiration from
% \cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
% \feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
% show that it satisfies our basic notion of delegatable anonymous credentials.
% Roughly, a delegatable anonymous credential scheme is an anononymous credential
% scheme in which every issuer of level $n$ can only issue credentials of level
% $n+1$. For simplicity, we restrict to the case of using only one credential per
% signature, but the generalization is trivial. Note that, in addition to the
% algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
% which, given an issuer's public key and its alleged level, returns $1$ if the
% level is correct, or $0$ otherwise.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.4\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        %(\opk,\osk) \gets \OKeyGen(\parm) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }
      \vspace*{0.75em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
%        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.6\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
          \Verify(\cdot,\cdot)\rangle$} \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        % D \cup \lbrace n+1 \rbrace)\rangle \\        
        \pcif \exists i \in [1,n]~\suchthat~
        \langle Show(\ipk_{i-1},\attrs(\cred_{i}),(i,D'),\cred_{i}), \\
        \hspace*{8em}Verify(\ipk_{i-1},(i,D')) \rangle
        = \langle \cdot,0\rangle \\%~\lor % \\
        % \pcind \attrs(\cred_i) \not\subseteq \attrs(\cred_{i-1}):
        \pcind \pcreturn 1 \\
%        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
%        \not\subseteq \ATTR[j])~\lor\\
%        \pcind level(\opk,n) = 0: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
    \lbrace HU,CU,HI,CI,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
    \gets \lbrace HU,CU,HI,CI,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent
    to \OBTCHALb in \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR
    and \ATTR tables are essentially as in \secref{ssec:model-uas}. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
only distinguish between top-level issuers, who have level $n=0$, and
lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
that the first attribute (after the user's secret key) encodes the level of
the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
addition, all users (i.e., with $n>0$) who want to delegate have to publicly
list:

\begin{enumerate}
\item The level $n$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $n$, and over
  the attributes that this level-$n$ issuer is delegating.
\item The \ipk of the parent issuer.
\item Their $\fissue^{n,\dattrs}$ function.
\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
Namely, the issuance function checks that the first requested attribute equals
$n+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$n$ issuer. In addition, signature
evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
must reveal the level of the credential used to produce the \UAS signature at
item 2, and reveal a set of attributes \dattrs that the level-$n$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Of course, additional checks may be added in both functions, this is
  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
that this structure creates.

\begin{align}
  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
    \rbrace \nonumber \\
  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
  \label{eq:funcs-dac}
\end{align}

From this high-level description, we define the algorithms of \CUASDAC:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
    be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
  where $\ipk^{n-1}$ is the public key of the parent issuer,
  $\fissue^{n,\dattrs}$ is an issuance function as described in
  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
  delegate..
\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
  credentials.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
  required by the issuer.
\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in \CUASGen. Concretely, arbitrary
  \feval functions can be used -- not necessarily $\feval^{n,\dattrs}$.
\end{description}

\iffalse
We adopt the simplification that the level of an issuer is encoded in its public
key, and anybody can check the issuer's level via some publicly accessible
mechanism. This can be ensured, e.g., by having each issuer post its
  public key along with a proof of ownership of a level $n$ credential -- which
  can be trivially done in \CUASGen.

### 2022-06-15 prism-backend/research/gsac/model-uas.tex
Seemingly valid construction of DAC from UAS. Proof pending.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of credentials \scred,
  each with a matching issuer key in \sipk.
  The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation
  function \feval, returns signature \sig, and a plaintext value \yeval. For
  readability, we use \Sig to denote the tuple $(\sig,\yeval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential \cred from an issuer in the system, on attribute
  set $\attrs$. The user leverages a set of credentials \scred, each with a
  matching issuer key in \sipk (ommitted in \Obtain for readability). The user
  outputs the produced credential \cred, while the issuer outputs the protocol
  transcript \utrans for the produced credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. For readability, we assume
  that, for each $\cred \in \scred$, we can get the corresponding issuer public
  key \ipk; also, we use use \Sig to denote the tuple $(\sig,\yeval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}
